### 2012-12-19 Docs/managing_jobs/managingjobs.tex
more hopper stuff

>>>>

\subsection{General Guidelines}

hopper is configured with 24 cores per node, with the cores grouped
into 4 NUMA nodes of 6 cores each.  Best performance is seen when
running with 6 threads and 4 MPI tasks per node, using the following
run line:
\begin{verbatim}
aprun -n 128 -N 4 -d 6 -S 1 -ss ./main.Linux.Cray.mpi.omp.ex inputs_3d
\end{verbatim}
Here, {\tt -n} is the number of MPI tasks, and {\tt n * d} is the
total number of cores (which should match the {\tt mppwidth} set at
the top of the submission script).
